---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SeffCovar

<!-- badges: start -->
<!-- badges: end -->

The goal of SeffCovar is to construct covariates for slide-effect-adjustment for epigenome-wide association studies.


## Installation

You can install SeffCovar using:

``` r
library(devtools)
install_github("julianhecker/SeffCovar")
```

## Example: Assessing S_high and S_80_100

```{r example_assess}
library(SeffCovar)
length(S_high)
length(S_80_100)
```


## Example: Construct slide effects covariates

This function returns 10 covariates. The number of covariates that need to be included in an association analysis depends 
and should evaluated in the respective study.

```{r example_covar}
methylation_matrix=matrix(rnorm(length(S_high)*100), nrow=length(S_high), ncol=100)
rownames(methylation_matrix)=S_high
slide_covars=get_slide_effects_covariates(methylation_matrix=methylation_matrix, input_set=S_high)
```






